Hierarchical Dispatching and Overriding

### 2017-09-19 NewVersion/sections/Formalization.tex
refine formalization text

\vspace{-2ex}
\subsection{Syntax}
Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small
subset of the interface model. For example, all the methods declared
in an interface are default methods, that is to say, they always
provide default implementations. 
%From this point we can view that we
%are actually modelling a class model that supports multiple
%inheritance. 
Object creation is directly supported via $\new I$. 
Fields and primitive types are not modelled in \MIM{}.

We use uppercase letters like $I, J, K$ for interface identifiers. 
Due to multiple inheritance, an interface can have a set of
super interfaces, where such a set can be empty. Each interface
has a set of method declarations. Each method body returns
an expression. As seen in Figure~\ref{fig:syntax}, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.

>>>>

\vspace{-2ex}
\subsection{Syntax}
The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
in an interface are default methods, that is to say, they always
provide default implementations. 
%From this point we can view that we
%are actually modelling a class model that supports multiple
%inheritance. 
Object creation is directly supported via $\new I$. 
Fields and primitive types are not modelled in \MIM{}.

The metavariables $I, J, K$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations. Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method. In order to achieve multiple inheritance, an interface can have a set of 
parent interfaces, where such a set can be empty. Each interface
has a set of method declarations. Each method body returns
an expression. As shown in Figure~\ref{fig:syntax}, we have introduced the
\kwoverride{} keyword to override an old implementation of the
method. If the interface that it overrides is exactly the enclosing
interface, then such a method is seen as ``originally defined''; otherwise
it is hierarchical overriding.
For simplicity, overloading is not modelled for methods, which
implies we can uniquely identify a method by its name.
